Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-09 GNproof.tex
move the degerate case out of the base case

%If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$. In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.

@@

We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.  If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set. Otherwise, $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$

>>>>

If $\Prop(j_m) = \emptyset$ then $J$ is automatically dependent since the corresponding column of $C(W)$ contains only zeros, so suppose henceforth that $\Prop(j_m) \neq \emptyset$. %In particular, this implies that $m>1$, since if $m=1$ we would have $\Prop(j_1) \subseteq \cP_0 = \emptyset$.

@@

We now proceed to prove $Q\subseteq \mathcal{P}_{m-1}$ by inductively proving $Q_l \subseteq \mathcal{P}_{m-1}$ for all $l \geq 0$.
%If $Q_0 = \Prop(j_m) = \emptyset$ then $Q = \emptyset$, and $I_i(Q) \cup \{j_m\}= \{j_m\}$ is a single vertex supporting no propagators, and thus a dependent set. Otherwise,
For the base case $Q_0 \subseteq \cP_{m-1}$ follows immediately from the first observation above that $\Prop(j_m) \subseteq \cP_{m-1}$
